### 2020-01-13 Article.tex
Mas pequeño

Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is

@@

We say that a connected hypergraph $G$ is \textbf{dense} if
$ex(G)>0$.
We want to show that a.a.s any sub-hypergraph 
of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ whose
diameter is small (i.e. bounded by some constant)
is not dense. \par
It takes a direct computation to show that given
an hypergraph $H$, the number of different (not necessarily
induced) sub-hypergraphs of $\mathrm{G}^\mathcal{C}(n,\overbar{p})$
isomorphic to $H$ belongs to $\Theta(n^{-ex(H)})$.
Indeed, let $N:=|V(H)|$ and let $\phi$ be the automorphism
group of $H$. Then, each sequence $v_1,\dots,v_N$ of $N$
different vertices in $[n]$ can either define a copy of $H$
in $\mathrm{G}^\mathcal{C}(n,\overbar{p})$ or not. Also, each
sequence

>>>>

Given two hypergraphs $G$ and $H$, a copy of $H$ in $G$ is
a sub-hypergraph $H_2\subseteq G$ isomorphic to $H$. The copy
is called induced if $H_2$ is an induced sub-hypergraph.
We will call a labeled copy
of $H$ in $G$ to a monomorphism $f:H\rightarrow G$. 
It is satisfied that the number
of labeled copies of $H$ in $G$ is $|Aut(H)|$ times the number
of copies of $H$ in $G$.

@@

We say that a connected hypergraph $G$ is \textbf{dense} if
$ex(G)>0$. Given $r\in \N$, we say that $G$ is \textbf{$r$-simple}
if $G$ does not contain any dense subgraph $H$ such that 
$diam(H)\leq r$. The goal of this section is to show that, for any
fixed $r$, a.a.s $G_n$ is $r$-simple.\par

\begin{lemma}
	Let $H$ be an hypergraph. Then 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big]=
	\Theta(n^{-ex(H)})$ as $n$ tends to infinity.  
\end{lemma}
\begin{proof}

Indeed, let $n\in \N$ and let $G_n$ be a random hypergraph sampled from
$\mathrm{G}^\mathcal{C}(n,\overbar{p})$. Let
$\overbar{h}$ be an ordering of the vertices
in $V(H)$. For any list 
$\overbar{v}\in [n]_{|V(H)|}$ (recall that $[n]=V(G)$), 
let $X_{\overbar{v}}$ be the random indicator variable
that takes value $1$ if the natural map 
$f:\overbar{h}\rightarrow \overbar{v}$ defines an homomorphism 
between $H$ and $G$. That is, $X_{\overbar{v}}$ takes value $1$
with probability
$ \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|},
$
and zero otherwise. The sum of all $X_{\overbar{v}}$'s for 
all $\overbar{v}\in [n]_{|V(H)|}$ counts how many labelled 
copies of $H$ are in $G_n$. Thus, 
\[ \mathrm{E}\big[\# \text{labelled copies of }H \text{ in } G_n\big] 
= \sum_{\overbar{v}\in [n]_{|V(G)|}} 
\prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
= (n)_{|V(H)|} \prod_{i=1}^{t} \big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}.
\]
The expected number of copies of $H$ in $G_n$ is then this last
expectation divided by the number of automorphisms of $H$, $|Aut(H)|$.
In consequence,
\begin{align*}
&\Ln \mathrm{E}\big[\# \text{copies of }H \text{ in } G_n\big] 
=\Ln \frac{(n)_{|V(H)|}}{|Aut(H)|} \prod_{i=1}^{t} 
\big(\beta_i n^{1-a_i} \big)^{|E_i(H)|}
=\\ &\Ln \Big[(n)_{|V(H)|}\prod_{i=1}^{t}n^{(1-a_i)|E_i(H)|}\Big]
\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|} \simeq \Ln
n^{-ex(H)}\frac{\prod_{i=1}^{t} \beta_i^{|E_i(H)|}}{|Aut(H)|},
\end{align*}
and last expression belongs to $\theta(n^{-ex(H)})$, as desired.\par
\end{proof}

As a corollary of last result we get the following:  
\begin{lemma} 
	Let $H$ be an hypergraph such that $ex(H)>0$. Then
	a.a.s there are no copies of $H$ in $G_n$. 
\end{lemma}  
\begin{proof}
	Because of the previous fact, 
	$\mathrm{E}\big[\# \text{ copies of }H \text{ in } G_n\big] 
	\xrightarrow[]{n\to \infty} 0$. Then an application of the first moment
	method yields the desired result. 
\end{proof}

The main theorem of this section is the following

\begin{lemma}
	Let $H$ be a dense hypergraph of radius $r$.
	Then $H$ contains a dense sub-hypergraph $H^\prime$ 
	with size no greater than
	$(a+2)(r+1)+2a$, where $a$ is the largest edge size in $H$. 
\end{lemma}
\begin{proof}
	Choose $x\in V(H)$. Successively remove from $G$ edges $e$
	such that $d(x, e)$ is maximum until the resulting graph 
	$H^\prime$ has excess no greater than $0$. We have two cases:
	\begin{itemize}[leftmargin=*]
		\item $ex(H^\prime)=-1$. Let $e=[x_1, \dots, x_b]$ be
		the last removed edge and
		$e\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$.
		For any $j=1,\dots, d$ choose 
		$P_j$ a path of size no greater than $r+1$ joining
		$x$ and $x_{i_j}$ in $H^\prime$.   
		Then $P_1\cup \dots P_d \cup e$ is a dense sub-hypergraph of $H$
		of size less than $a(r+1) + a< (a+2)(r+1) + 2a$.
		\item $ex(H^\prime)=0$. Let $e_1=[x_1, \dots, x_{b_1}]$ be the
		last removed edge. Continue removing the edges of $G^\prime$ 
		that are at maximum distance from $x$ until you obtain 
		$H^{\prime \prime}$ with $ex(H^{\prime\prime})=-1$. Let 
		$e_2=[y_1, \dots, y_{b_2}]$ be the last removed edge this time.
		As before, let $e_1\cap H^\prime=\{ x_{i_1}, \dots, x_{i_d}\}$
		and for $j=1,\dots, d$ let $P_j$ a path of size no greater than $r+1$ 
		joining	$x$ and $x_{i_j}$ in $H^\prime$
		Then $e_2 \cup H^{\prime \prime}=\{ y_{i_1}, y_{i_2}  \}$.
		Let $Q_1, Q_2$ be paths size no greater than $r+1$ from
		$x$ to $y_{i_1}$ and $y_{i_2}$ in $H^{\prime \prime}$.
		Then $Q_1 \cup Q_2 \cup e_2$ is a graph of likelihood $0$ 
		and size less than $2r+2 + a$,
		and $Q_1\cup Q_2\cup P_1 \cup \dots \cup P_d \cup e_1 \cup e_2$ 
		is a critical graph	with size less than $(2+a)(r+1) + 2a$	
	\end{itemize} 
\end{proof}

\begin{theorem}
	Let $r\in \N$. Then a.a.s $G_n$ is $r$-simple. 
\end{theorem}
\begin{proof}
	The first moment method alone is not sufficient
	to prove our claim because the amount of dense 
	hypergraphs	$H$ such that $diam(H)\leq r$ is not finite
	in general. Thus, we need to prove that it suffices to
	prohibit a finite amount of dense sub-hypergraphs in order
	to guarantee that $G_n$ is $r$-simple.
\end{proof}
